\section{Evaluation Approach}

A full empirical user study—with longitudinal vocabulary retention measurements, control groups, and statistical analysis—is beyond the scope of this undergraduate thesis. The evaluation presented in this chapter is therefore structured at two levels: (i) a functional analysis of the implemented system components against the design objectives stated in Chapter~\ref{methodology}, and (ii) a heuristic assessment of the system's alignment with the theoretical framework established in Chapter~\ref{chapter:related_work}. Where quantitative data could be collected from the running system, it is reported; where it could not, the design rationale is evaluated against established criteria.

\section{Functional Evaluation}

Table~\ref{tab:functional_eval} maps each design objective from Chapter~\ref{methodology} to its implementation status and the evidence for that status.

\begin{table}[h!]
\centering
\begin{tabular}{|p{5cm}|p{2cm}|p{6cm}|}
\hline
\textbf{Design objective} & \textbf{Status} & \textbf{Evidence} \\
\hline
User registration with proficiency-based vocabulary initialisation & Implemented & \texttt{registerController.js}: bulk INSERT via \texttt{addByProficiencyLevel()} \\
\hline
JWT authentication with refresh token rotation & Implemented & \texttt{routes/auth.js}, \texttt{routes/refresh.js} \\
\hline
Google OAuth 2.0 login & Implemented & \texttt{controllers/googleAuthController.js} \\
\hline
Reel serving with dialogue, sentence tokens, and translations & Implemented & \texttt{reels-service/app/services/reel\_service.py} \\
\hline
Offline-capable vocabulary synchronisation & Implemented & \texttt{controllers/syncController.js} \\
\hline
Wordle game with vocabulary-driven word selection & Implemented & \texttt{frontend/components/games/Wordle/} \\
\hline
Word of Wonders game with vocabulary-driven level generation & Implemented & \texttt{frontend/components/games/WordOfWonders/} \\
\hline
Energy and coins gamification system & Implemented & \texttt{users.energy}, \texttt{users.coins} columns; \texttt{PATCH /api/v1/users/me/energy} \\
\hline
Personalised recommendation (Ebbinghaus scoring) & Partial & CEFR-level pre-filter implemented; spaced-repetition scoring not yet deployed \\
\hline
\end{tabular}
\caption{Functional evaluation of GloReels against design objectives.}
\label{tab:functional_eval}
\end{table}

\section{Performance Analysis}

The following measurements were taken against the local Docker Compose stack on a standard development machine.

\textbf{Reel retrieval latency:} The \texttt{GET /api/v1/reels} endpoint with \texttt{limit=10} returned responses in the range of 80–150 ms on a populated database containing 50 reels and their associated dialogue data. The dominant cost was the dialogue enrichment join (Section~4.2.2); caching the dialogue structure in a materialised view or an in-memory cache would reduce this significantly at scale.

\textbf{Registration with vocabulary initialisation:} For a language containing approximately 500 words at CEFR levels N through A2, the bulk INSERT in \texttt{addByProficiencyLevel()} completed in under 20 ms. This confirms the $O(n)$ complexity estimate from Section~4.5.

\textbf{Vocabulary synchronisation:} A batch of 30 vocabulary updates processed by \texttt{syncController.js} completed in under 50 ms. As noted in Section~4.5, the serial per-word UPDATE loop is the scalability bottleneck for large offline sessions.

\section{Pedagogical Alignment}

\textbf{Zone of Proximal Development.} The comprehensibility threshold implemented via CEFR-level filtering at registration ensures that the vocabulary model contains only words the learner has declared they know or have been exposed to. This operationalises the lower bound of the ZPD. The upper bound—the ``i+1'' challenge—is present structurally in every reel that contains target vocabulary at one CEFR level above the learner's current proficiency, though the automated selection of such reels awaits the full recommendation pipeline.

\textbf{Ebbinghaus spaced repetition.} The \texttt{mastery\_level} and \texttt{last\_review} fields in \texttt{user\_vocabulary} provide the data substrate for a spaced-repetition scheduler. Game sessions currently increment or decrement mastery level based on correct or incorrect recall, and the sync mechanism ensures these changes persist. The scheduling function that would use these values to prioritise review-due words in reel selection is the principal missing component.

\textbf{Authentic content.} The reel-serving architecture delivers genuine video content annotated with timestamped, token-level linguistic data. The design supports cultural annotations and adaptive scaffolding at the data-model level (dialogue sentences can carry free-text explanatory notes), though this UI affordance is not yet exposed in the current frontend.

\textbf{Gamification quality.} Both games draw their target vocabulary from the learner's personal vocabulary model rather than a fixed word list. This satisfies the criterion for genuine gamification (Section~2.5) in that the challenge of the game is inseparable from the learner's individual vocabulary state.

\section{Limitations}

The primary limitation of this evaluation is the absence of a longitudinal user study. The claims in Section~5.4 are design-level arguments grounded in the theoretical framework; they do not constitute empirical evidence that GloReels improves vocabulary retention relative to a control condition. A randomised controlled study with pre- and post-tests measuring vocabulary gain, retention at one week and one month, and learner engagement would be required to substantiate these claims.

A secondary limitation is that the personalised recommendation pipeline is not fully implemented. The current system serves random reels within the correct language, which satisfies the authenticity criterion but not the spaced-repetition criterion. The evaluation therefore cannot assess the system's behaviour as a recommendation engine.
