% Glossary of Terms — must remain in alphabetical order

\textbf{Authentic materials} --- Language learning resources drawn from real-world communicative situations, produced by native speakers for native speakers rather than created artificially for instructional purposes.

\textbf{CEFR level} --- A proficiency descriptor from the Common European Framework of Reference for Languages, ranging from A1 (beginner) through C2 (mastery). Used in GloReels to tag words and to initialise the learner's vocabulary model.

\textbf{Cognitive Load Theory} --- An instructional design theory that distinguishes between intrinsic load (complexity of the material), extraneous load (demands from poor design), and germane load (effort directed at schema formation). Effective instruction minimises extraneous load.

\textbf{Dialogue} --- In the GloReels schema, a structured sequence of sentences associated with a reel, carrying per-sentence video timestamps that enable synchronised subtitle rendering.

\textbf{Ebbinghaus forgetting curve} --- An empirical model of memory decay showing that retention drops exponentially over time without review. The basis for spaced-repetition scheduling systems.

\textbf{Energy system} --- A gamification mechanism in GloReels that limits the number of game rounds per session, preventing cognitive overload and encouraging regular short sessions rather than infrequent long ones.

\textbf{Hypercasual game} --- A game genre characterised by a single core mechanic, minimal learning curve, and session lengths of one to five minutes, suited to mobile use during short breaks.

\textbf{Mastery level} --- A value from 1 to 6 stored in \texttt{user\_vocabulary} that represents a learner's degree of familiarity with an individual word, from initial exposure (1) to durable active recall (6).

\textbf{Microservice} --- An architectural pattern in which a system is decomposed into small, independently deployable services, each responsible for a specific domain. GloReels uses this pattern to separate the reels pipeline from the main backend API.

\textbf{Reel} --- A short-form video clip, typically under 90 seconds, drawn from a social media platform or user-generated content. In GloReels, each reel is annotated with a full linguistic dialogue.

\textbf{Scaffolding} --- Temporary instructional support provided to a learner to enable them to accomplish a task they could not yet perform independently, progressively removed as competence develops.

\textbf{Spaced repetition} --- A learning technique in which review of material is scheduled at increasing time intervals, calibrated to the moment immediately before forgetting occurs, to consolidate long-term retention.

\textbf{Token} --- In computational linguistics, a single word or punctuation unit identified within a sentence. In the GloReels schema, \texttt{sentence\_tokens} links each sentence to its constituent words with position and part-of-speech information.

\textbf{Zone of Proximal Development (ZPD)} --- Vygotsky's concept of the gap between what a learner can do independently and what they can achieve with guidance. Effective instruction targets this zone. In GloReels, the 98\% vocabulary comprehensibility threshold is the operational proxy for the ZPD lower bound.
